### 2021-04-14 main.tex
Use a non-breaking space after "no."

This work was supported by
the Czech Science Foundation project no.~20-06390Y (JUNIOR grant),
the project RICAIP no. 857306 under the EU-H2020 programme,
and
the Grant Agency of the Czech Technical University in Prague, grant
no.~SGS20/215/OHK3/3T/37.

>>>>

This work was supported by
the Czech Science Foundation project no.~20-06390Y (JUNIOR grant),
the project RICAIP no.~857306 under the EU-H2020 programme,
and
the Grant Agency of the Czech Technical University in Prague, grant
no.~SGS20/215/OHK3/3T/37.
